---
title: "R Notebook"
output: html_notebook
---

#1. Creates a vector v of 100 elements with the command v <- rnorm (100). 
#For this vector, print: the 10th element; elements from the 10th to the 20th inclusive;
#10 elements starting from the 20th; items greater than 0.

```{r}
v <- rnorm(100)
a1 <- v[10]
print(a1)
```
```{r}
v <- rnorm(100)
a2 <- v[10:20]
print(a2)
```
```{r}
v <- rnorm(100)
x3 <- 10
a3 <- v[20:(20+x3-1)]
print(a3)
```
```{r}
v <- rnorm(100)
a4 <- v[v>0]
print(a4)
```
#2. Create data frame y with the command y <- data.frame (a = rnorm (100), b = 1: 100,
#cc = sample (letters, 100, replace = TRUE)). To do this, print the data frame: the last 10 lines; 
#terms from 10 to 20 inclusive; 10th element of column b; the entire cc column, using the column name.

```{r}
y <- data.frame(a = rnorm(100), b = 1:100, cc = sample(letters, 100, replace = TRUE))
y1 = y2-9
y2 = nrow(y)
b2 <- y[(nrow(y)-9):nrow(y),]
print(b2)
```

```{r}
y <- data.frame(a = rnorm(100), b = 1:100, cc = sample(letters, 100, replace = TRUE))
b3 <- y[10:20,]
print(b3)
```

```{r}
y <- data.frame(a = rnorm(100), b = 1:100, cc = sample(letters, 100, replace = TRUE))
b4 <- y[c(10),c(2)]
print(b4)
```

```{r}
y <- data.frame(a = rnorm(100), b = 1:100, cc = sample(letters, 100, replace = TRUE))
b5 <- data.frame(y$cc)
print(b5)
```

#3. Create a vector z with elements 1, 2, 3, NA, 4, NA, 5, NA. For this vector: output all elements 
#that are not NA; calculate the average of all elements of this vector without NA values and with NA values.

```{r}
z <- c(1, 2, 3, NA, 4, NA, 5, NA)
z1 <- z[!is.na(z)]
print(z1)
```
```{r}
z <- c(1, 2, 3, NA, 4, NA, 5, NA)
meanz = mean(z, na.rm = TRUE)
meanz2 = mean(z)
print(meanz)
print(meanz2)
```




