---
title: "R Notebook"
output: html_notebook
---
#In laboratory work it is necessary to write the following functions in R language
#and to deduce result of work of these functions on arbitrary data:

#1. The add2 (x, y) function, which returns the sum of two numbers.
```{r}
add2 <- function(x,y)
{
  return(x+y)
}

add2(10,5)
```
#2. A function above (x, n) that takes a vector and a number n and returns all 
#elements of the vector that are greater than n. The default is n = 10.
```{r}
above <- function(x,n=10)
  {
  return (x[x > n])
  }

above(x = c(8:13),n = 9)
```
#3. The my_ifelse (x, exp, n) function, which takes the vector x, compares all 
#its elements with exp to n, and returns the elements of the vector that correspond
#to the expression condition. For example, my_ifelse (x, “>”, 0) returns all elements
#of x that are greater than 0. Exp can be equal to “<”, “>”, “<=”, “> =”, “==”. If exp
#does not match any of these expressions, the vector x is returned.

```{r}
my_ifelse <- function(x, exp, n)
{
  if (exp == '<')
  return(x[x<n])
  else if (exp == '>')
  return(x[x>n])
  else if (exp == '<=')
  return(x[x<=n])
  else if (exp == '>=')
  return(x[x>=n])
  else if (exp == '==')
  return(x[x==n])
  else
  return(x)
}
x = c(20:40)
n = 30
my_ifelse(x,'>=',n)
```
#4. The columnmean (x, removeNA) function, which calculates the mean value for 
#each column of the matrix, or data frame. The removeNA logical parameter 
#specifies whether to delete the NA value. By default, it is TRUE.
```{r}
columnmean <- function(x, removeNA)
{
  if (removeNA == TRUE)
    return(colMeans(x, na.rm=TRUE))
  else
    return(colMeans(x))
}
x <- matrix(c(6:14,NA,17:19, NA, 20),ncol=3, nrow=5)
removeNA = TRUE
columnmean(x,removeNA)
```